Analysis of bulk void regions

### 2014-07-01 cosmic_voids.tex
Adding volume function of voids in paper tex file
Updating pdf paper

%.........................................................................
%FIGURE 3: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering

>>>>

%.........................................................................
%FIGURE 3: volume functions
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}

  \captionof{figure}{\small Volume functions of voids catalogued by each 
  used scheme. Left panel (watershed transform over the FA field of the T-web 
  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
  (over the density field). Gray curves correspond to voids without boundary 
  removal whereas black curves are associated to voids merged through boundary 
  removal process. Dotted lines correspond to original continuous fields, 
  while segmented lines correspond to fields with a 1st-order median filtering 
  and continuous lines to a 2nd-order median filtering.}

%.........................................................................
%FIGURE 4: FA and vissual impression
\begin{flushleft}
\begin{figure*}
\centering
